### 2022-05-10 manuscript.tex
the real submitted version :tada: :rocket:
affiliation corrections and file renaming + reference final PDF

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Ten simple rules to host an inclusive conference} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Rocío Joo\textsuperscript{1*\Yinyang}, 
Andrea Sánchez-Tapia\textsuperscript{2\Yinyang},
Sara Mortara\textsuperscript{3},
Yanina Bellini Saibene\textsuperscript{4,5},
Heather Turner\textsuperscript{6}, %\ddag},
Dorothea Hug Peter\textsuperscript{7}, %\ddag},
Natalia Soledad Morandeira\textsuperscript{8},
Matt Bannert\textsuperscript{9},
Batool Almazrouq\textsuperscript{10},
Elizabeth Hare\textsuperscript{11},
Laura Ación\textsuperscript{5,12},
Juan Pablo Narváez-Gómez\textsuperscript{13},
Marcela Alfaro Córdoba\textsuperscript{14},
Federico Marini\textsuperscript{15},
Rita Giordano\textsuperscript{16},
Silvia Canelón\textsuperscript{17},
Anicet Ebou\textsuperscript{18},
Adithi Upadhya\textsuperscript{19},
Joselyn Chávez\textsuperscript{20},
Janani Ravi\textsuperscript{21*}
%,3\textcurrency}
\\
\bigskip
\textbf{1} Global Fishing Watch, Washington, DC 20036, USA
\\
\textbf{2} Instituto de Pesquisas Jardim Botânico do Rio de Janeiro, Rio de Janeiro, Rio de Janeiro, Brazil
\\
\textbf{3} International Institute for Sustainability, Rio de Janeiro, Rio de Janeiro, Brazil
\\
\textbf{4} Instituto Nacional de Tecnología Agropecuaria, Ruta Nac. N° 5, Km. 580, Anguil, La Pampa, Argentina; Universidad Nacional Guillermo Brown, Buenos Aires, Argentina
\\
\textbf{5} MetaDocencia, Argentina
\\
\textbf{6} Department of Statistics, University of Warwick, Coventry, UK; The R Foundation
\\
\textbf{7} Swiss Federal Institute for Forest, Snow and Landscape Research WSL, Birmensdorf, Switzerland
\\
\textbf{8} Instituto de Investigación e Ingeniería Ambiental, Universidad Nacional de San Martín - Consejo Nacional de Investigaciones Científicas y Técnicas, General San Martín, Buenos Aires, Argentina
\\
\textbf{9} KOF Swiss Economic Institute, ETH Zurich, Zurich, Switzerland
\\
\textbf{10} Institute of Systems, Molecular and Integrative Biology, University of Liverpool, Liverpool, L69 7ZB, UK; King Abdullah International Medical Research Center, Riyadh, Saudi Arabia
\\
\textbf{11} Dog Genetics LLC, Astoria, NY, USA
\\
\textbf{12} Instituto de Cálculo, FCEyN, UBA-CONICET, Buenos Aires, Argentina
\\
\textbf{13} Departamento de Botânica, Instituto de Biociências, Universidade de São Paulo, São Paulo, São Paulo, Brasil
\\
\textbf{14} Department of Statistics, University of California, Santa Cruz, CA, USA
\\
\textbf{15} Institute of Medical Biostatistics, Epidemiology and Informatics (IMBEI), University Medical Center Mainz, Mainz, Germany
\\
\textbf{16} Royal Society of Chemistry, Thomas Graham House (290), Science Park, Milton Road, Cambridge, UK
\\
\textbf{17} Department of Biostatistics, Epidemiology \& Informatics, University of Pennsylvania, Philadelphia, PA, USA.
\\
\textbf{18} Bioinformatics team, Département de Formation et de Recherches en Agriculture et Ressources Animales, Institut National Polytechnique Félix Houphouët-Boigny, BP 1313 Yamoussoukro, Côte d’Ivoire.
\\
\textbf{19} ILK Labs, Bengaluru, Karnataka, 560046, India
\\
\textbf{20} Instituto de Biotecnología, UNAM, Cuernavaca, Morelos, México
\\
\textbf{21} Departments of Pathobiology and Diagnostic Investigation, Microbiology and Molecular Genetics, Michigan State University, East Lansing, MI 48824, USA
\\
\bigskip

@@

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Ten simple rules to host an inclusive conference} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Rocío Joo\textsuperscript{1*\Yinyang}, 
Andrea Sánchez-Tapia\textsuperscript{2\Yinyang},
Sara Mortara\textsuperscript{3},
Yanina Bellini Saibene\textsuperscript{4,5},
Heather Turner\textsuperscript{6}, %\ddag},
Dorothea Hug Peter\textsuperscript{7}, %\ddag},
Natalia Soledad Morandeira\textsuperscript{8},
Matt Bannert\textsuperscript{9},
Batool Almazrouq\textsuperscript{10},
Elizabeth Hare\textsuperscript{11},
Laura Ación\textsuperscript{5,12},
Juan Pablo Narváez-Gómez\textsuperscript{13},
Marcela Alfaro Córdoba\textsuperscript{14},
Federico Marini\textsuperscript{15},
Rita Giordano\textsuperscript{16},
Silvia Canelón\textsuperscript{17},
Anicet Ebou\textsuperscript{18},
Adithi Upadhya\textsuperscript{19},
Joselyn Chávez\textsuperscript{20},
Janani Ravi\textsuperscript{21*}
%,3\textcurrency}
\\
\bigskip
\textbf{1} Global Fishing Watch, Washington, DC 20036, USA
\\
\textbf{2} Instituto de Pesquisas Jardim Botânico do Rio de Janeiro, Rio de Janeiro, Rio de Janeiro, Brazil
\\
\textbf{3} International Institute for Sustainability, Rio de Janeiro, Rio de Janeiro, Brazil
\\
\textbf{4} Instituto Nacional de Tecnología Agropecuaria, Ruta Nac. N° 5, Km. 580, Anguil, La Pampa, Argentina; Universidad Nacional Guillermo Brown, Buenos Aires, Argentina
\\
\textbf{5} MetaDocencia, Argentina
\\
\textbf{6} Department of Statistics, University of Warwick, Coventry, UK; The R Foundation
\\
\textbf{7} Swiss Federal Institute for Forest, Snow and Landscape Research WSL, Birmensdorf, Switzerland
\\
\textbf{8} Instituto de Investigación e Ingeniería Ambiental, Universidad Nacional de San Martín - Consejo Nacional de Investigaciones Científicas y Técnicas, General San Martín, Buenos Aires, Argentina
\\
\textbf{9} KOF Swiss Economic Institute, ETH Zurich, Zurich, Switzerland
\\
\textbf{10} Institute of Systems, Molecular and Integrative Biology, University of Liverpool, Liverpool, L69 7ZB, UK; King Abdullah International Medical Research Center, Riyadh, Saudi Arabia
\\
\textbf{11} Dog Genetics LLC, Astoria, NY, USA
\\
\textbf{12} Instituto de Cálculo, FCEyN, UBA-CONICET, Buenos Aires, Argentina
\\
\textbf{13} Departamento de Botânica, Instituto de Biociências, Universidade de São Paulo, São Paulo, São Paulo, Brasil
\\
\textbf{14} Department of Statistics, University of California, Santa Cruz, CA, USA
\\
\textbf{15} Institute of Medical Biostatistics, Epidemiology and Informatics (IMBEI), University Medical Center Mainz, Mainz, Germany
\\
\textbf{16} Royal Society of Chemistry, Thomas Graham House (290), Science Park, Milton Road, Cambridge, UK
\\
\textbf{17} Department of Biostatistics, Epidemiology \& Informatics, University of Pennsylvania, Philadelphia, PA, USA.
\\
\textbf{18} Bioinformatics team, Département de Formation et de Recherche Agriculture et Ressources Animales, Institut National Polytechnique Félix Houphouët-Boigny, Yamoussoukro, Côte d’Ivoire.
\\
\textbf{19} ILK Labs, Bengaluru, Karnataka, 560046, India
\\
\textbf{20} Instituto de Biotecnología, UNAM, Cuernavaca, Morelos, México
\\
\textbf{21} Departments of Pathobiology and Diagnostic Investigation, Microbiology and Molecular Genetics, Michigan State University, East Lansing, MI 48824, USA
\\
\bigskip

@@

The funders had no role in study design, decision to publish, or preparation of the manuscript.

### 2022-05-10 reference_PDF.tex
affiliation corrections and file renaming + reference final PDF

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Ten simple rules to host an inclusive conference} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Rocío Joo\textsuperscript{1*\Yinyang}, 
Andrea Sánchez-Tapia\textsuperscript{2\Yinyang},
Sara Mortara\textsuperscript{3},
Yanina Bellini Saibene\textsuperscript{4,5},
Heather Turner\textsuperscript{6}, %\ddag},
Dorothea Hug Peter\textsuperscript{7}, %\ddag},
Natalia Soledad Morandeira\textsuperscript{8},
Matt Bannert\textsuperscript{9},
Batool Almazrouq\textsuperscript{10},
Elizabeth Hare\textsuperscript{11},
Laura Ación\textsuperscript{5,12},
Juan Pablo Narváez-Gómez\textsuperscript{13},
Marcela Alfaro Córdoba\textsuperscript{14},
Federico Marini\textsuperscript{15},
Rita Giordano\textsuperscript{16},
Silvia Canelón\textsuperscript{17},
Anicet Ebou\textsuperscript{18},
Adithi Upadhya\textsuperscript{19},
Joselyn Chávez\textsuperscript{20},
Janani Ravi\textsuperscript{21*}
%,3\textcurrency}
\\
\bigskip
\textbf{1} Global Fishing Watch, Washington,  District of Columbia, United States of America
\\
\textbf{2} Instituto de Pesquisas Jardim Botânico do Rio de Janeiro, Rio de Janeiro, Rio de Janeiro, Brazil
\\
\textbf{3} International Institute for Sustainability, Rio de Janeiro, Rio de Janeiro, Brazil
\\
\textbf{4} Instituto Nacional de Tecnología Agropecuaria, Ruta Nac. N° 5, Km. 580, Anguil, La Pampa, Argentina; Universidad Nacional Guillermo Brown, Buenos Aires, Argentina
\\
\textbf{5} MetaDocencia, Argentina
\\
\textbf{6} Department of Statistics, University of Warwick, Coventry, UK; The R Foundation
\\
\textbf{7} Swiss Federal Institute for Forest, Snow and Landscape Research WSL, Birmensdorf, Switzerland
\\
\textbf{8} Instituto de Investigación e Ingeniería Ambiental, Universidad Nacional de San Martín - Consejo Nacional de Investigaciones Científicas y Técnicas, General San Martín, Buenos Aires, Argentina
\\
\textbf{9} KOF Swiss Economic Institute, ETH Zurich, Zurich, Switzerland
\\
\textbf{10} Institute of Systems, Molecular and Integrative Biology, University of Liverpool, Liverpool, L69 7ZB, UK; King Abdullah International Medical Research Center, Riyadh, Saudi Arabia
\\
\textbf{11} Dog Genetics LLC, Astoria, New York, United States of America
\\
\textbf{12} Instituto de Cálculo, FCEyN, UBA-CONICET, Buenos Aires, Argentina
\\
\textbf{13} Departamento de Botânica, Instituto de Biociências, Universidade de São Paulo, São Paulo, São Paulo, Brazil
\\
\textbf{14} Department of Statistics, University of California, Santa Cruz, California, United States of America
\\
\textbf{15} Institute of Medical Biostatistics, Epidemiology and Informatics (IMBEI), University Medical Center Mainz, Mainz, Germany
\\
\textbf{16} Royal Society of Chemistry, Thomas Graham House (290), Science Park, Milton Road, Cambridge, UK
\\
\textbf{17} Department of Biostatistics, Epidemiology \& Informatics, University of Pennsylvania, Philadelphia, Pennsylvania, United States of America.
\\
\textbf{18} Bioinformatics team, Département de Formation et de Recherches en Agriculture et Ressources Animales, Institut National Polytechnique Félix Houphouët-Boigny, BP 1313 Yamoussoukro, Côte d’Ivoire.
\\
\textbf{19} ILK Labs, Bengaluru, Karnataka, India
\\
\textbf{20} Instituto de Biotecnología, UNAM, Cuernavaca, Morelos, Mexico
\\
\textbf{21} Departments of Pathobiology and Diagnostic Investigation, Microbiology and Molecular Genetics, Michigan State University, East Lansing, Michigan, United States of America
\\
\bigskip

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Ten simple rules to host an inclusive conference} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Rocío Joo\textsuperscript{1*\Yinyang}, 
Andrea Sánchez-Tapia\textsuperscript{2\Yinyang},
Sara Mortara\textsuperscript{3},
Yanina Bellini Saibene\textsuperscript{4,5},
Heather Turner\textsuperscript{6}, %\ddag},
Dorothea Hug Peter\textsuperscript{7}, %\ddag},
Natalia Soledad Morandeira\textsuperscript{8},
Matt Bannert\textsuperscript{9},
Batool Almazrouq\textsuperscript{10},
Elizabeth Hare\textsuperscript{11},
Laura Ación\textsuperscript{5,12},
Juan Pablo Narváez-Gómez\textsuperscript{13},
Marcela Alfaro Córdoba\textsuperscript{14},
Federico Marini\textsuperscript{15},
Rita Giordano\textsuperscript{16},
Silvia Canelón\textsuperscript{17},
Anicet Ebou\textsuperscript{18},
Adithi Upadhya\textsuperscript{19},
Joselyn Chávez\textsuperscript{20},
Janani Ravi\textsuperscript{21*}
%,3\textcurrency}
\\
\bigskip
\textbf{1} Global Fishing Watch, Washington, District of Columbia, United States of America
\\
\textbf{2} Instituto de Pesquisas Jardim Botânico do Rio de Janeiro, Rio de Janeiro, Rio de Janeiro, Brazil
\\
\textbf{3} International Institute for Sustainability, Rio de Janeiro, Rio de Janeiro, Brazil
\\
\textbf{4} Universidad Nacional Guillermo Brown, Buenos Aires, Argentina; Instituto Nacional de Tecnología Agropecuaria, Anguil, La Pampa, Argentina; R-Ladies, California, United States of America  
\\
\textbf{5} MetaDocencia, Ciudad Autónoma de Buenos Aires, Argentina
\\
\textbf{6} Department of Statistics, University of Warwick, Coventry, UK; The R Foundation for Statistical Computing, Vienna, Austria
\\
\textbf{7} Mountain Hydrology and Mass Movements, Swiss Federal Institute for Forest, Snow and Landscape Research WSL, Birmensdorf, Switzerland
\\
\textbf{8} Instituto de Investigación e Ingeniería Ambiental, Universidad Nacional de San Martín - Consejo Nacional de Investigaciones Científicas y Técnicas, General San Martín, Buenos Aires, Argentina
\\
\textbf{9} KOF Swiss Economic Institute, ETH Zurich, Zurich, Switzerland
\\
\textbf{10} Institute of Systems, Molecular and Integrative Biology, University of Liverpool, Liverpool, UK; King Abdullah International Medical Research Center, Riyadh, Saudi Arabia
\\
\textbf{11} Dog Genetics LLC, Astoria, New York, United States of America
\\
\textbf{12} Instituto de Cálculo, Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires - Consejo Nacional de Investigaciones Científicas y Técnicas, Ciudad Autónoma de Buenos Aires, Argentina
\\
\textbf{13} Departamento de Botânica, Instituto de Biociências, Universidade de São Paulo, São Paulo, São Paulo, Brazil
\\
\textbf{14} Department of Statistics, University of California, Santa Cruz, California, United States of America
\\
\textbf{15} Institute of Medical Biostatistics, Epidemiology and Informatics (IMBEI), University Medical Center Mainz, Mainz, Germany
\\
\textbf{16} Royal Society of Chemistry, Thomas Graham House (290), Science Park, Milton Road, Cambridge, UK
\\
\textbf{17} Department of Biostatistics, Epidemiology \& Informatics, University of Pennsylvania, Philadelphia, Pennsylvania, United States of America.
\\
\textbf{18} Bioinformatics team, Département de Formation et de Recherche Agriculture et Ressources Animales, Institut National Polytechnique Félix Houphouët-Boigny, Yamoussoukro, Côte d’Ivoire.
\\
\textbf{19} ILK Labs, Bengaluru, Karnataka, India
\\
\textbf{20} Instituto de Biotecnología, UNAM, Cuernavaca, Morelos, Mexico
\\
\textbf{21} Departments of Pathobiology and Diagnostic Investigation, Microbiology and Molecular Genetics, Michigan State University, East Lansing, Michigan, United States of America
\\
\bigskip
